Reduce Latex Spacing

### 2020-01-27 _support/spacing/reduce/reduce.tex
Equation gap control specific group

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}

\usepackage{amsfonts}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Reduce Spacing for Math Equations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\g@addto@macro\normalsize{%
  \setlength\abovedisplayskip{1pt}
  \setlength\belowdisplayskip{1pt}
  \setlength\abovedisplayshortskip{1pt}
  \setlength\belowdisplayshortskip{1pt}
}

@@

>>>>

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{amsfonts}

@@

@@

\subsection{Code to Change Equation Spacing in One Spot}
\begin{lstlisting}
  {
  \abovedisplayskip=25pt
  \belowdisplayskip=25pt
  \abovedisplayshortskip=5pt
  \belowdisplayshortskip=5pt
  let's skip a lot on top
  \begin{align*}
    \begin{gathered}
          1+1=2\\
          2+2=4
  \end{gathered}
  \end{align*}  
  let's skip not skip a lot at the bottom
  }
\end{lstlisting}
{
  \abovedisplayskip=125pt
  \belowdisplayskip=125pt
  \abovedisplayshortskip=5pt
  \belowdisplayshortskip=5pt
  let's skip a lot on top
  \[
  1+1=2
  \]
  let's skip not skip a lot at the bottom
}

\subsection{Change Equation Spacing Different Equations}

Some types of equations one spacing, others another.

\begin{lstlisting}
\newcommand{\assumptionskip}{
\abovedisplayskip=6pt
\belowdisplayskip=6pt
\abovedisplayshortskip=6pt
\belowdisplayshortskip=6pt
}
\newcommand{\theoremskip}{
\abovedisplayskip=12.0pt plus 3.0pt minus 7.0pt
\belowdisplayskip=12.0pt plus 3.0pt minus 7.0pt
\abovedisplayshortskip=0.0pt plus 3.0pt
\belowdisplayshortskip=6.5pt plus 3.5pt minus 3.0pt
}
{
\assumptionskip
\begin{assumption}
\label{as:2a}
Let $A$ be an $i$ specific function with input $b$, specifically:
\begin{align*}
	\begin{gathered}
        1+1=2\\
        2+2=4\\
\end{gathered}
\end{align*}
where the effects of binary input $B$ on $C$ is additively separable from $Z$.
\end{assumption}
}

\end{lstlisting}

see: \href{https://www.overleaf.com/learn/latex/%5Cabovedisplayskip%20and%20related%20commands}{abovedisplayskip and related commands}
